Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/hotspot-one-chromosome.Rmd
fixed definition of local traits for a hotspot
started using knitr::knit_expand instead of child = ...

# Chr `r hot_chr`

```{r}
hot_lower <- hot_mid - 2
hot_upper <- hot_mid + 2
fp <- paste0("Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = here("analysis", "figures", fp))
```

```{r}
pleio_mixed_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_pleio.rds")))
pleio_local_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_pleio_local.rds")))
pleio_nonlocal_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_pleio_nonlocal.rds")))
med_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_mediations.rds")))
```

```{r}
local_annot <- lod_peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(local_tx)
```

@@

```{r}
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper + 1, middle >= hot_lower - 1) %>% 
  arrange(desc(lod))
```

@@

```{r}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == keller_mediator, nonlocal = nonlocal_symbol, local = local_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

>>>>

# Chr {{hot_chr}}

```{r, def-{{hot_chr}}}
hot_lower <- hot_mid - 2
hot_upper <- hot_mid + 2
fp <- paste0("Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = here("analysis", "figures", fp))
```

```{r, readRDS-{{hot_chr}}}
pleio_mixed_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_pleio.rds")))
pleio_local_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_pleio_local.rds")))
pleio_nonlocal_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_pleio_nonlocal.rds")))
med_list <- readRDS(here("analysis", "data", "derived_data", paste0("Chr", hot_chr, "_mediations.rds")))
```

```{r, define_local_annot-{{hot_chr}}}
local_annot <- lod_peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= ult) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(local_tx)
```

@@

```{r}
local_annot2 <- local_annot %>%
  filter(middle <= hot_upper, middle >= hot_lower) %>% 
  arrange(desc(lod))
```

@@

```{r, scatter-{{hot_chr}}}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == keller_mediator, nonlocal = nonlocal_symbol, local = local_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

### 2019-08-02 analysis/paper/hotspots-paper.Rmd
started using knitr::knit_expand instead of child = ...

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: 
  bookdown::html_document2:
  code_folding: hide  
---

@@

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
linkReferences: true
link-citations: true
output: 
  - bookdown::html_document2:
    code_folding: hide
  - bookdown::pdf_document2:
    code_folding: hide  
---

@@

```{r}
knitr::knit_expand(file = here::here("analysis", "paper", "hotspot-one-chromosome.Rmd"))
```
